PSE Quant Sampling Algorithm

### 2021-02-25 quant_estimate/pse_quant_algo.tex
Draft-1 Edit
Draft-1 Edit (Add Optimize)

\usepackage{algorithm,algpseudocode}

\algnewcommand{\algorithmicforeach}{\textbf{for each}}
\algdef{SE}[FOR]{ForEach}{EndForEach}[1]
{\algorithmicforeach\ #1\ \algorithmicdo}% \ForEach{#1}
{\algorithmicend\ \algorithmicforeach}% \EndForEach
\usepackage{listings}
\usepackage{xcolor} % for setting colors

% set the default code style
\lstset{
	frame=tb, % draw a frame at the top and bottom of the code block
	tabsize=4, % tab space width
	showstringspaces=false, % don't mark spaces in strings
	numbers=left, % display line numbers on the left
	commentstyle=\color{red}, % comment color
	keywordstyle=\color{blue}, % keyword color
	stringstyle=\color{gray} % string color
}

\begin{document}
\begin{lstlisting}[language=C++, caption={C++ code using listings}]
int main(void)
{
	int a, d;
	// forall variable
	klee_make_symbolic(&a, sizeof(a), "a_sym");
	// PSE variable : Uniformly distributed [0 to 650]
	make_pse_symbolic<int>(&d, sizeof(d), "d_prob_sym", 0, 650);
	int c = a + 100;

	// case 1
	if (a > 50)	{
		c = a + 75;
	}	else	{
		c = a - 75;
	}

	// case 2
	if (d > 60)
		d = 250;

	// case 3 -> Complex Case
	if (c > d)
		c = d;

	return 0;
}
\end{lstlisting}
\begin{algorithm}
    \caption{Complex Case : (Testing Based Estimation)}
    \begin{algorithmic}[1]
        \ForEach{$a \in A$}%
        \State command \algorithmiccomment{This is a comment}
        \State another command \algorithmiccomment{This is another comment}
        \EndForEach
    \end{algorithmic}
\end{algorithm}

>>>>

\usepackage{algorithm, algpseudocode}

\algnewcommand{\algorithmicforeach}{\textbf{for each}}
\algdef{SE}[FOR]{ForEach}{EndForEach}[1]
{\algorithmicforeach\ #1\ \algorithmicdo}% \ForEach{#1}
{\algorithmicend\ \algorithmicforeach}% \EndForEach
\usepackage{minted}

\title{PSE Quant Sampling Algorithm}
\author{Sumit Lahiri}

\begin{document}
	\maketitle

We try to formulate a way to compute path probabilities using \texttt{symbolic execution} and \texttt{testing} based technique.  
\begin{minted}{c} 
int main(void)
{
	int a; // unintialized
	int d = std::uniform_distribution<rd_seed>(0, 650);

	// forall variable : (INT_MIN to INT_MAX)
	klee_make_symbolic(&a, sizeof(a), "a_sym");

	// PSE variable : Uniformly distributed [0 to 650]
	make_pse_symbolic<int>(&d, sizeof(d), "d_prob_sym", 0, 650);

	int c = a + 100;

	// case 1 : Pure Forall Predicate
	if (a > 50) {
	  c = a + 75;
	} else {
	  c = a - 75;
	}

	// case 2 : Pure PSE Predicate
	if (d > 60) d = 250;

	// case 3 : Dependence Case
	if (c > d) c = d;

	// Probabilistic query : assert(P(c != d) < 0.5)
	// Opitimize here : 
	//	Optimal value of forall (a) such that P(c != d) is close to 0.5 	
	return 0;
}
\end{minted}

\begin{algorithm}[H]
    \caption{Dependence Case : (Testing Based Estimation)}
    \begin{algorithmic}[1]
        \ForEach{$p \in Paths$}%
        \State $c := ConstraintSet(p)$ \algorithmiccomment{Path Constraints for p}
        \State $m := Optimize(query,  c)$ \algorithmiccomment{solution for the path constraints}
        \State $concreteSet = \{ \}$
        	\ForEach{$v \in ForallVars(p)$} \algorithmiccomment{ForallVars p $\rightarrow $ forall} %
        	\State $concreteSet.append(\{key : v, val : m[v]\})$ \algorithmiccomment{Candidate Values}
        	\EndForEach
        \State $executeCV(program, concreteSet)$
        \EndForEach
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
	\caption{executeCV : PSE Sampled Normal Execution}
	\begin{algorithmic}[1]
		\Function{executeCV}{$P : program, C : concreteSet$}
			\ForEach{$v \in ForallVars(p)$}%
			\State value(v) := concreteSet(v) \algorithmiccomment{Use values from ConcreteSet}
			\EndForEach
			\State ... \algorithmiccomment{proceed with normal execution}
		\EndFunction
	\end{algorithmic}
\end{algorithm}
